### 2016-03-20 ch03-lrm/smoothingRMSdecrease.tex
Some small things

\newcommand{\segm}[2]{\ensuremath{{#1}^{[#2]}}}
\newcommand{\RMS}{\ensuremath{\,\mathrm{rms}\,}}
\newcommand{\rms}[1]{\ensuremath{\RMS\left(#1\right)}}
\newcommand{\floor}[1]{\ensuremath{\lfloor #1 \rfloor}}

@@

  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \cite{Parsons1974}, while accounting for the degrees of freedom in each segment.
  For zero-mean noise, these variances can be related to the RMS value of each noise segment.
  This has the advantage that a segment in which the impulse response still has a significant amplitude is likely to have a large RMS value, which is more likely to be detected.
  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \emph{viz}:
  \begin{equation}
    s^2(i) = \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
           = \left( \rms{\hat{g}^{[i]}} \right)^2
           \text{.}
  \end{equation}
  Starting with the last segment ($i = N_S$), the following null hypothesis and the alternative hypothesis are formulated:
  \begin{align}
     H_0 :&\,\, s^2(i-1) = s^2(i)\\
     H_1 :&\,\, s^2(i-1) > s^2(i)
     \text{.}
  \end{align}
  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise, the null hypothesis states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
  The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
  Using the $F$-test on the RMS values of the two segments with a high confidence level of $\alpha=0.99$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
  The high level of confidence ($\alpha=0.99$) ensures that the probability of a Type~II error is smaller than $1-\alpha$ \cite{Parsons1974}.
  In our case, such an error means that a part of the actual impulse response would falsely be regarded as noise, which could significantly increase the bias as information of the system is discarded.
  A Type~I error is less detrimental since, in that case, noise is falsely classified as a signal component and kept in the impulse response, thereby causing a sub-optimal value of the variance of the estimate.
  As the LPM samples are correlated over a short frequency span, the actual noise present in $\hat{g}$ may be slightly non-stationary.
  To cope with this, one can introduce other criteria which must be satisfied together with the outcome of the $F$-test.
  A criterion that shows good results is to check whether the segment $\segm{\hat{g}}{i-1}$ has an RMS value that is at least a factor $\kappa$ larger than the RMS of the noise.
  Even for a moderate $\kappa = 1.1$, a large improvement in the detection was observed. 
%  \JL{Q: doesn't this increase the probability of a Type II error?}
%  \EG{A: This slightly increases for small $\kappa$ and increases significantly for large values of $\kappa$. But it is needed to overcome nonstationarity of the noise.}

@@

\begin{figure}[tbh]
\centering
 \setlength\figureheight{0.6\columnwidth}
 \setlength\figurewidth{0.8\columnwidth}
  \input{truncRMS.tikz}
\caption{Schematic of statistical determination of a smooth (improved) FRF. The different segments are separated by dotted lines.}
\label{FRF_truncate_stat_EG}
\end{figure}

>>>>

\newcommand{\segm}[2]{\ensuremath{{#1}^{[#2]}}}

@@

  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \citep{Parsons1974}, while accounting for the degrees of freedom in each segment.
  For zero-mean noise, these variances can be related to the RMS value of each noise segment.
  This has the advantage that a segment in which the impulse response still has a significant amplitude is likely to have a large RMS value, which is more likely to be detected.
  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \emph{viz}:
  \begin{equation}
    s^2(i) 
    \isdef \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
    = \left( \rms{\hat{g}^{[i]}} \right)^2
           \text{.}
  \end{equation}
  Starting with the last segment ($i = N_S$), the following null hypothesis and the alternative hypothesis are formulated:
  \begin{align}
     \nullHypothesis &: s^2(i-1) = s^2(i)\\
     \altHypothesis    &: s^2(i-1) > s^2(i)
     \text{.}
  \end{align}
  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise, the null hypothesis states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
  The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
  Using the $F$-test on the RMS values of the two segments with a high confidence level of $\alpha=0.99$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
  The high level of confidence ($\alpha=0.99$) ensures that the probability of a Type~II error is smaller than $1-\alpha$ \citep{Parsons1974}.
  In our case, such an error means that a part of the actual impulse response would falsely be regarded as noise, which could significantly increase the bias as information of the system is discarded.
  A Type~I error is less detrimental since, in that case, noise is falsely classified as a signal component and kept in the impulse response, thereby causing a sub-optimal value of the variance of the estimate.
  As the LPM samples are correlated over a short frequency span, the actual noise present in $\hat{g}$ may be slightly non-stationary.
  To cope with this, one can introduce other criteria which must be satisfied together with the outcome of the $F$-test.
  A criterion that shows good results is to check whether the segment $\segm{\hat{g}}{i-1}$ has an RMS value that is at least a factor $\kappa$ larger than the RMS of the noise.
  Even for a moderate $\kappa = 1.1$, a large improvement in the detection was observed. 
%  \JL{Q: doesn't this increase the probability of a Type II error?}
%  \EG{A: This slightly increases for small $\kappa$ and increases significantly for large values of $\kappa$. But it is needed to overcome nonstationarity of the noise.}

@@

\begin{figure}[tbh]
\centering
 \setlength\figureheight{0.6\columnwidth}
 \setlength\figurewidth{0.8\columnwidth}
  \input{\thisDir/figs/truncRMS.tikz}
\caption{Schematic of statistical determination of a smooth (improved) FRF. 
The different segments are separated by dotted lines.}
\label{FRF_truncate_stat_EG}
\end{figure}

### 2016-03-20 ch05-initvals/initial-values.tex
'linear zoom' in captions
Some small things

  With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$.
  In this chapter, we limit the notations to quadratic polynomials in a window with half-width $n=3$, such that
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
\true{G}(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
\end{align}
\end{subequations}
where, in general,$\ r\in\mathbb{W}_n,\quad$$\mathbb{W}_n = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. 
\TODO{notatie LPM uniform maken met CH03/CH04}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\columnwidth}
  \input{\thisDir/fig/CostFunctionsMLE-measurement.tikz}
  \caption[Cost function values over the different measurements.]{Cost function values $V(\theta)$ obtained during the different realizations of the measurement.
  The bottom plot shows a zoom of the top plot.
  For each method, the inter-quartile range~\legref{leg:costMeasurements:best:iqr}, median~\legref{leg:costMeasurements:best:median} and individual values~\legref{leg:costMeasurements:best:data} are shown.
  This implies that a lower (local) minimum of the cost function can be attained using these smoothing techniques.}
  \label{fig:costMeasurements}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\columnwidth}
  \input{\thisDir/fig/meas-validation.tikz}
  \caption[Validation cost of the different measurements.]{Validation of the measured models. 
  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
  $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
  The bottom plot shows a zoom of the top plot.
  The proposed methods yield models that are closer to $\model{VXI}$ than the existing $\model{exist}$.
  The results are in line with the values of the cost function in \figref{fig:costMeasurements}.}
  \label{fig:validationMeasurements}
\end{figure}
\begin{table}[p]
  \centering
  \caption{Observed percentiles of the validation distance $\norm{\model{\bullet}-G_{\mathrm{VXI}}}$.}
  \input{\thisDir/tables/meas-validation-quantiles.tbl.tex}
\label{tbl:validationMeasurements}
\end{table}

>>>>

  With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$.
  In this chapter, we limit the notations to quadratic polynomials in a window with half-width $n=3$, such that
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
\true{G}(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
\end{align}
\end{subequations}
where, in general,$\ r\in \LocalShifts[]$ with $\LocalShifts[] = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. 
\TODO{notatie LPM uniform maken met CH03/CH04}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\columnwidth}
  \input{\thisDir/fig/CostFunctionsMLE-measurement.tikz}
  \caption[Cost function values over the different measurements.]{Cost function values $V(\theta)$ obtained during the different realizations of the measurement.
  The bottom plot shows a linear zoom of the top plot.
  For each method, the inter-quartile range~\legref{leg:costMeasurements:best:iqr}, median~\legref{leg:costMeasurements:best:median} and individual values~\legref{leg:costMeasurements:best:data} are shown.
  This implies that a lower (local) minimum of the cost function can be attained using these smoothing techniques.}
  \label{fig:costMeasurements}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\columnwidth}
  \input{\thisDir/fig/meas-validation.tikz}
  \caption[Validation cost of the different measurements.]{Validation of the measured models. 
  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
  $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
  The bottom plot shows a linear zoom of the top plot.
  The proposed methods yield models that are closer to $\model{VXI}$ than the existing $\model{exist}$.
  The results are in line with the values of the cost function in \figref{fig:costMeasurements}.}
  \label{fig:validationMeasurements}
\end{figure}
\begin{table}[p]
  \centering
  \caption{Observed percentiles of the validation distance $\norm{\model{\bullet}-G_{\mathrm{VXI}}}$.}
  \input{\thisDir/tables/meas-validation-quantiles.tbl.tex}
\label{tbl:validationMeasurements}
\end{table}
